%-------------------------
% Resume in LaTeX
% Author : Adapted for Asim Shafique
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Asim Shafique} \\ \vspace{2pt}
    +92 325 4155556 $|$ 
    \href{mailto:asimshafique59@gmail.com}{asimshafique59@gmail.com} $|$ 
    \href{https://github.com/AsimShafique-59}{GitHub} $|$ 
    \href{https://www.linkedin.com/in/muhammad-asim-shafique-0581411aa}{LinkedIn} $|$ 
    \href{https://asimshafique.netlify.app/}{Portfolio}
\end{center}

%-----------PROFILE-----------
\section{Profile}
Dedicated Python AI Engineer specializing in backend development, Django REST Framework, FastAPI, and generative AI engineering. Experienced in building scalable LLM-powered applications using LangChain, LangGraph, CrewAI, OpenAI Agent SDK, vector databases, and production-ready automation systems.

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

%==================== Hashed Systems ====================
\resumeSubheading
{\textbf{Hashed Systems}}{Present}
{Python Django Developer}{Lahore, Pakistan}
\resumeItemListStart
  \resumeItem{Designed, developed, and maintained production-grade backend systems using Python, Django, and Django REST Framework (DRF).}
  \resumeItem{Architected and optimized RESTful APIs with JWT authentication, role-based access control (RBAC), and secure authorization workflows.}
  \resumeItem{Led PostgreSQL database design, schema migrations, indexing strategies, and query performance optimization.}
  \resumeItem{Implemented robust CRUD operations, data validation, structured error handling, and API testing using Postman.}
\resumeItemListEnd

%==================== Web Excels ====================
\resumeSubheading
{\textbf{WEB EXCELS}}{November 2025 -- January 2026}
{AI Engineer}{Lahore, Pakistan}
\resumeItemListStart
  \resumeItem{Developed AI-driven backend applications using Python, LangChain, OpenAI API, and vector database technologies.}
  \resumeItem{Designed and optimized LLM pipelines for chatbots, data extraction, and automation workflows.}
  \resumeItem{Integrated AI models into production backend systems with scalability, data validation, and monitoring.}
  \resumeItem{Performed prompt engineering, model evaluation, and iterative accuracy improvements for conversational agents.}
\resumeItemListEnd

%==================== Artificizen ====================
\resumeSubheading
{\textbf{ARTIFICIZEN}}{April 2025 -- September 2025}
{Software Engineer – Backend \& AI Systems}{Lahore, Pakistan}
\resumeItemListStart
  \resumeItem{Designed and developed intelligent chatbot systems using LangChain, LangGraph, CrewAI, and OpenAI SDK.}
  \resumeItem{Built backend services with Python, Django, and DRF, integrating database systems and JWT authentication.}
  \resumeItem{Developed and tested RESTful APIs for AI system integration using Postman and automated test workflows.}
  \resumeItem{Collaborated with cross-functional teams to deliver AI-driven backend solutions aligned with business requirements.}
\resumeItemListEnd

%==================== AB IT ====================
\resumeSubheading
{\textbf{AB IT and Technical Services Limited}}{June 2024 -- June 2025}
{Python Backend Developer}{United Kingdom (Remote)}
\resumeItemListStart
  \resumeItem{Designed and implemented backend systems using Python, Django, and DRF with PostgreSQL, MySQL, and MongoDB integration.}
  \resumeItem{Developed scalable RESTful APIs and backend services with secure JWT/OAuth2 authentication.}
  \resumeItem{Containerized and deployed applications using Docker and implemented CI/CD pipelines with GitHub Actions / GitLab CI.}
  \resumeItem{Ensured code quality, version control, and production stability across cloud and remote environments.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Reachgin -- Multi-Industry POS}}{2026}
\resumeItemListStart
  \resumeItem{Architected a scalable backend system (35+ apps, 150+ models) for a multi-industry POS platform with centralized admin management.}
  \resumeItem{Implemented RESTful APIs with JWT authentication (SimpleJWT), token rotation, blacklisting, and role-based access control.}
  \resumeItem{Designed a service-layer architecture with UUID primary keys, soft deletes, transaction management, invoicing, and promotions.}
  \resumeItem{Integrated asynchronous task queues (Celery, Redis), cloud storage (AWS S3), push notifications (Firebase FCM), and OpenAPI documentation.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Venuze -- Venue Booking Platform}}{2026}
\resumeItemListStart
  \resumeItem{Built scalable REST APIs with FastAPI, PostgreSQL, SQLAlchemy, and Redis, including JWT auth and token blacklisting.}
  \resumeItem{Developed venue booking workflows with AWS S3 media uploads, availability calendars, invoices, coupon systems, dispute handling, and real-time chat.}
  \resumeItem{Integrated Stripe payments, OAuth2 login, Firebase notifications, and optimized async performance using asyncio and background workers.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Power Email AI}}{2025}
\resumeItemListStart
  \resumeItem{Engineered an AI email automation system with intelligent reply generation, inbox routing, sequences, campaigns, and rule-based workflows.}
  \resumeItem{Developed modular backend services with JWT auth, encrypted credential storage, and AWS SES email automation.}
  \resumeItem{Built AI-driven features for context-aware response generation and accuracy improvements using OpenAI-powered pipelines.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Peer Learning Circle Web Application}}{2025}
\resumeItemListStart
  \resumeItem{Built a Django-based collaboration platform for students to create and manage study groups with customized admin controls.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Sophia Bot -- AI Healthcare Assistant}}{2025}
\resumeItemListStart
  \resumeItem{Developed a healthcare chatbot with context-aware responses, conversation history tracking, and integration-ready architecture for EHR workflows.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://drive.google.com/file/d/1aIIAQlgccWA_iy6n1lcNw9FU-gNtkcXa/view}{Qualifi Level 5 Diploma in Information Technology}}{2025}
    {Qualifi (UK Accredited)}{Lahore, Pakistan}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\resumeItemListStart
\resumeItem{\textbf{Languages \& Frameworks:} Python, SQL, Django, DRF, FastAPI, Flask, JavaScript, HTML, CSS.}
\resumeItem{\textbf{AI \& LLM Engineering:} LangChain, LangGraph, CrewAI, OpenAI SDK, Gemini, Groq, RAG, vector databases, embeddings, semantic search, chatbot pipelines, agentic AI systems.}
\resumeItem{\textbf{Backend Architecture:} REST APIs, microservices, JWT auth, WebSockets, async processing, Celery, event-driven systems, clean architecture.}
\resumeItem{\textbf{Databases \& Storage:} PostgreSQL, MySQL, MongoDB, SQLite, Chroma, Pinecone, FAISS, advanced SQL design and optimization.}
\resumeItem{\textbf{Cloud \& DevOps:} AWS (S3, EC2), Google Cloud, Alibaba Cloud, Docker, Vercel, Render, GitHub Actions, Git, Postman.}
\resumeItem{\textbf{Operating Systems:} Ubuntu Linux, Windows.}
\resumeItem{\textbf{Soft Skills:} Agile collaboration, problem-solving, system design, technical documentation, product-minded engineering.}
\resumeItemListEnd

%-----------LANGUAGES-----------
\section{Languages}
\resumeItemListStart
\resumeItem{English}
\resumeItem{Urdu}
\resumeItem{German}
\resumeItemListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\resumeItemListStart
\resumeItem{\textbf{IELTS Academic:} Overall Band Score -- 6.0}
\resumeItemListEnd

\end{document}
